Analysis of Major Crimes in Toronto And Suggestions on How to Protect Ourselves

### 2024-01-23 outputs/paper/paper.qmd
Change the structure of the paper

```{r}
#| include: false
clean_mci_data <- clean_mci_data |> 
  mutate(
    weekday_weekend =
      case_match(
        occ_dow,
        "Wednesday" ~ "Weekday",
        "Tuesday" ~ "Weekday",
        "Thursday" ~ "Weekday",
        "Sunday" ~ "Weekend",
        "Monday" ~ "Weekday",
        "Friday" ~ "Weekday",
        "Saturday" ~ "Weekend",
        "" ~ "Other"))
clean_mci_data
```
There are 18 police divisions, which are D11, D12, D13, D14, D22, D23, D31, D32, D33, D41, D42, D43, D51, D52, D53, D54, D55, and NSA. I put them into 6 geographical regions, Etobicoke-York, Etobicoke, North York, Scarborough, Toronto-East York, and other, as shown in Table 2.Based on Figure 2, Toronto-East York reports the highest amount of crimes, and Etobicoke-York has the lowest. North York, Scarborough, and Etobicoke-York have similar numbers, but the rate of increase in North York is higher than that observed in the other two. 
```{r}
#| message: false
#| echo: false
#| label: tbl-division_area
#| tbl-cap: Police divisions in 6 areas(including other)

@@

```{r}
#| message: false
#| echo: false
#| label: fig-time_of_crimes
#| fig-cap: Number of Crimes in a Day
clean_mci_data |>
  filter(weekday_weekend == 'Weekday' | weekday_weekend == 'Weekend') |>
  count(occ_hour, weekday_weekend) |>
  ggplot(mapping = aes(x = occ_hour, y = n, color = weekday_weekend)) +
  geom_line() +
  theme(legend.position = "top") +
  labs(x = "Time In a Day", y = "Number of Crimes", color = "Weekday or Weekend") +
  scale_color_manual(values = c("Weekday" = "steelblue3", "Weekend" = "indianred3"))
```
Figure 3 indicates the preferred time to commit crimes. The graph reveals a higher likelihood of criminal behaviours during the evening, with occurrences steadily increasing as the night progresses towards midnight and afterwards, the occurrences decrease until six in the morning. Interestingly, there is a surprising local peak at noon, while 11:00 and 13:00 do not show a high probability.

@@

\newpage
# Conclusion
In summary, ‘Assault’ has always ranked as the most common major crime over the past ten years. However, the difference between ‘Auto Theft’ and ‘Assault’ is shrinking, as the number of ‘Auto Theft’ is increasing rapidly. There need be more safety actions on automobiles, and people should lock the doors and not leave any packages visible through car windows to improve automobile security. Due to the difficulty to prove ‘Assault’ as a crime, installing cameras at the front door or home security systems is a good idea to provide evidence for ‘Assault’, while it can also record suspicious individuals and vehicles near one's residence. Taking proactive steps, such as responding to knocks cautiously while keeping the door locked, and refraining from touching anything until the police have inspected, is crucial for personal safety and should be instilled in children as well.

>>>>

```{r}
#| include: false
clean_mci_data <- clean_mci_data |> 
  mutate(
    weekday_weekend =
      case_match(
        occ_dow,
        "Wednesday" ~ "Weekday",
        "Tuesday" ~ "Weekday",
        "Thursday" ~ "Weekday",
        "Sunday" ~ "Weekend",
        "Monday" ~ "Weekday",
        "Friday" ~ "Weekday",
        "Saturday" ~ "Weekend",
        "" ~ "Other"))
clean_mci_data
```
There are 18 police divisions, which are D11, D12, D13, D14, D22, D23, D31, D32, D33, D41, D42, D43, D51, D52, D53, D54, D55, and NSA. I put them into 6 geographical regions, Etobicoke-York, Etobicoke, North York, Scarborough, Toronto-East York, and other, as shown in Table 2. Based on Figure 2, Toronto-East York reports the highest amount of crimes, and Etobicoke-York has the lowest. North York, Scarborough, and Etobicoke-York have similar numbers, but the rate of increase in North York is higher than that observed in the other two. 
```{r}
#| message: false
#| echo: false
#| label: tbl-division_area
#| tbl-cap: Police divisions in 6 areas(including other)

@@

```{r}
#| message: false
#| echo: false
#| label: fig-time_of_crimes
#| fig-cap: Number of Crimes in a Day
clean_mci_data |>
  filter(weekday_weekend == 'Weekday' | weekday_weekend == 'Weekend') |>
  count(occ_hour, weekday_weekend) |>
  ggplot(mapping = aes(x = occ_hour, y = n, color = weekday_weekend)) +
  geom_line() +
  theme(legend.position = "top") +
  labs(x = "Time In a Day", y = "Number of Crimes", color = "Weekday or Weekend") +
  scale_color_manual(values = c("Weekday" = "steelblue3", "Weekend" = "indianred3"))
```
\newpage
Figure 3 indicates the preferred time to commit crimes. The graph reveals a higher likelihood of criminal behaviours during the evening, with occurrences steadily increasing as the night progresses towards midnight and afterwards, the occurrences decrease until six in the morning. Interestingly, there is a surprising local peak at noon, while 11:00 and 13:00 do not show a high probability.

@@

# Conclusion
In summary, ‘Assault’ has always ranked as the most common major crime over the past ten years. However, the difference between ‘Auto Theft’ and ‘Assault’ is shrinking, as the number of ‘Auto Theft’ is increasing rapidly. There need be more safety actions on automobiles, and people should lock the doors and not leave any packages visible through car windows to improve automobile security. Due to the difficulty to prove ‘Assault’ as a crime, installing cameras at the front door or home security systems is a good idea to provide evidence for ‘Assault’, while it can also record suspicious individuals and vehicles near one's residence. Taking proactive steps, such as responding to knocks cautiously while keeping the door locked, and refraining from touching anything until the police have inspected, is crucial for personal safety and should be instilled in children as well.
